systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-06-08 paper/trunk/systemfit_code.tex
changed paper according to changes of the package: systemfitClassic does not longer exist, but this kind of analysis can now be done directly in systemfit (if argument data is of class "pdata.frame")
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@730 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The \pkg{systemfit} package includes functions
to estimate systems of equations
(\code{systemfit}, \code{systemfitClassic}).
Furthermore, this package provides some methods
to test hypotheses
(\code{ftest}, \code{wald\-test},
\code{lrtest}, \code{hausman}),
to extract the estimated coefficients (\code{coef})
and to calculate predicted values (\code{predict}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection[Basic function systemfit]{The basic function \code{systemfit}}
The basic functionality of this package is provided by the
function \code{systemfit}.
This function estimates the equation system as described
in sections~\ref{sec:Estimation}.
If parameter restrictions are provided, the formulas in
section~\ref{sec:Restrictions} are applied.
Furthermore, the user can control several details of the estimation.
For instance, the
formula to calculate the residual covariance matrix
(see section~\ref{sec:residcov}),
the degrees of freedom for the $t$ tests
(see section~\ref{sec:degreesOfFreedom}), or
the formula for the 3SLS estimation
(see sections~\ref{sec:Estimation} and~\ref{sec:Restrictions})
can be specified by the user.
The \code{systemfit} function returns many objects
that users might be interested in.
A complete list is available in the documentation of this function
that is included in the package.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection[Wrapper function systemfitClassic]{The wrapper function
   \code{systemfitClassic}}
Furthermore, the \pkg{systemfit} package includes the function
\code{systemfitClassic}.
This is a wrapper function for \code{systemfit}
that can be applied to (classical) panel-like data in long format
if the regressors are the same for all equations.
The data are reshaped and the formulas are modified to enable
an estimation using the standard \code{systemfit} function.
The user can specify whether the coefficients should be restricted
to be equal in all equations.

>>>>

The most important function in the \pkg{systemfit} package
is called \code{systemfit}.
It can be used to estimate systems of linear equations
by several different estimation methods.
Furthermore, this package provides some methods
to test hypotheses
(\code{ftest}, \code{wald\-test},
\code{lrtest}, \code{hausman}),
to extract the estimated coefficients (\code{coef})
and to calculate predicted values (\code{predict}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection[Basic function systemfit]{The basic function \code{systemfit}}
The basic functionality of this package is provided by the
function \code{systemfit}.
This function estimates the equation system as described
in sections~\ref{sec:Estimation}.
If parameter restrictions are provided, the formulas in
section~\ref{sec:Restrictions} are applied.
Furthermore, the user can control several details of the estimation.
For instance, the
formula to calculate the residual covariance matrix
(see section~\ref{sec:residcov}),
the degrees of freedom for the $t$ tests
(see section~\ref{sec:degreesOfFreedom}), or
the formula for the 3SLS estimation
(see sections~\ref{sec:Estimation} and~\ref{sec:Restrictions})
can be specified by the user.
If \code{systemfit} is applied to
a (classical) °Seemingly Unrelated Regression° analysis with panel-like data,
it calls the hidden internal function \code{.systemfitPanel},
which reshapes the data, creates the formulas to be estimated,
and --- if requested --- specifies restrictions
to ensure that the parameters of all individuals are equal.

The \code{systemfit} function returns many objects
that users might be interested in.
A complete list is available in the documentation of this function
that is included in the package.
